---
title: "Votes Margin Analysis"
author: "Apoorv Anand"
date: "2021-12-30"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r source-files, include=FALSE}
source("code/source-libraries.R")
source("code/leaflet-options.R")
source("code/merge-data-gis.R")
```

# Introduction

Analysing the margin of votes by which a candidate wins the election is an important parameter for citizen and even the political parties especially in case of a seat which is decided by low margins. In this section of the analysis, we will explore the variable `margin ratio` which is calculated as the ratio of `margin of votes` ( _difference in the number of votes between winning candidate and the runner up_ ) to `total valid votes in a constituency`.

An example to illustrate how margin ratio works:

Case 1:

Total Votes: 1000
Win Margin: 500 - The winning candidate received 500 more votes than the runner-up
**Margin Ratio** = 500/1000 = 0.5 

Case 2:

Total Votes: 1000
Win Margin: 200
**Margin Ratio** = 200/1000 = 0.2

_A lower margin ratio signifies a tight contest whereas a high margin ratio points towards a more one-sided election._

## Analysis - How many constituencies had a margin ratio of less than 10%

```{r graph-margin-ratio, echo=FALSE}

color_bins <- c(0,5,15,25,35,50,Inf)
pal <- colorBin(palette = map_colour_palette,domain = constituency_map_file$margin_ratio,bins = color_bins)

labels <- sprintf(
  "<strong>%s</strong><br/> Margin Ratio: %s",
  stringr::str_to_title(constituency_map_file$constituency_name_dm),
  comma(constituency_map_file$margin_ratio, accuracy = 1,suffix = "%")) %>% 
  lapply(htmltools::HTML)

constituency_map_file %>% leaflet() %>%
  addTiles() %>%
  addPolygons(
    color = "white",
    opacity = 1,
    weight = 1,
    dashArray = "2",
    smoothFactor = 0.3,
    fillColor =  pal(constituency_map_file$margin_ratio),
    fillOpacity = 1,
    label = labels,
    highlightOptions = highlightOptions(
    weight = 2,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE)
  ) %>% 
  addLegend(
    pal = pal,
    values = ~ margin_ratio,
    opacity = 0.7,
    title = NULL,
    position = "bottomright"  
    )

```


